---
title: "Week1 - GSWR examples"
author: "Erika"
date: "5/18/2020"
output: html_document
---

This week, we're working on GSWR Chapter 2 on importing data and examining it with the dplyr package. I have provided three data sets, located in dropbox in Research Group -> Shared -> Cole.

Set up the workspace. Clear the workspace and load the dplyr and ggplot packages.
```{r}
rm(list = ls())
library(dplyr)
library(ggplot2)

```
Navigate to the folder Cole and use the "read.csv" function to load the dataset called "Cam_Use_Date.csv". Name the dataframe "DF".

```{r}
path<- "/Users/ebar/Dropbox/1Courses/ResearchGroup/Shared/Cole/SLU fellowship/Data/"
DF<-read.csv(paste0(path,"Cam_Use_Date.csv"))
```
How many rows of data?  How many variables?

Which variables come in as integers? characters? factors? dates? numerics?

Now load the same dataset again, but this time, use the following code: 
```{r}

DF1<- read.csv(paste0(path,"Cam_Use_Date.csv"), stringsAsFactors = T)
```
How did this change the structure of your data frame?

Use the names(), head(), dim(), and str() functions to examine DF.  What do you learn from each?

```{r}
names(DF)
```
```{r}
head(DF)
```
```{r}
dim(DF)
```
```{r}
str(DF)
```
Now load the dplyr package, if it isn't loaded already, and use it to run the glimpse() and tbl_df() functions.  What do these do?  How is their output similar to /different from the other functions you've used thus far?

```{r}
glimpse(DF)
```
```{r}
tbl_df(DF)
```





