---
title: "Getting Started with R chapter 3 - Camera trap data examples"
output: html_notebook
---

Prep your R workspace by writing code that will 1) clear R's brain, 2) turn on dplyr and 3) turn on ggplot:

```{r}
rm(list = ls())
library(dplyr)
library(ggplot2)
```
Load the data set called "masterDF_test.csv" and call the data frame "DF"

```{r}
DF<-read.csv("/Users/ebar/Dropbox/1Courses/ResearchGroup/Shared/Cole/SLU Fellowship/Data/masterDF_test.csv")
```
Review from chapter 2: Examine the dataset using the `str` function 
```{r}
str(DF)
```
Let's add a new variable to our data set, Class, which identifies the Class to which each species belongs. It will be a categorical variable, with 2 levels: Mammalia for all the mammals and Aves for the birds.  


1. Use `which` to determine the rows in DF that contain birds.
```{r}
birds<-c("GROUSERUFFED", "CROWORRAVEN", "OTHERBIRD", "OWL", "BLUEJAY", "TURKEY", "GOOSEWILD")

birdrows<- which(DF$bin %in% birds)

```
Now assign those rows to the Class Aves, creating a new column in the dataframe along the way.
```{r}
DF$Class<- "Mammalia" #creates new column and fills it with mammalia by default
DF$Class[birdrows]<- "Aves"
```
Now use `filter` and `group_by` to summarize the number of birds and mammals observed, respectively, by round.

```{r}
DF %>% filter(Class == "Mammalia") %>% group_by(round) %>% summarize(
  num_mammals = length(bin)
) 

DF %>% filter(Class == "Aves") %>% group_by(round) %>% summarize(
  num_birds = length(bin))

```

Now create a new data frame that contains only the members of the weasel family (mustelidae) from round 4 of the study

```{r}
mustelids<-c("FISHER", "WEASEL", "RIVEROTTER", "MINK")
weasels<-DF %>% filter(bin %in% mustelids & round == 4)
```

Now create a new data frame that contains only the turkeys from round 4 as well as the deer from rounds 2 or 3
```{r}
turkeydeer<-DF %>% filter(
  (bin %in% "TURKEY" & round == 4) |  
  (bin %in% "DEERWHITETAILED" & round == 2) | 
  (bin %in% "DEERWHITETAILED" & round == 3)
)
```




