---
title: "Getting Started with R chapter 3 - Camera trap data examples"
output: html_notebook
---

Prep your R workspace by writing code that will 1) clear R's brain, 2) turn on dplyr and 3) turn on ggplot:

```{r}
rm(list = ls())
library(dplyr)
library(ggplot2)
```
Load the data set called "masterDF_test.csv" and call the data frame "DF"

```{r}
DF<-read.csv("/Users/ebar/Dropbox/1Courses/ResearchGroup/Shared/Cole/SLU Fellowship/Data/masterDF_test.csv")
```
Review from chapter 2: Examine the dataset using the `glimpse` and `head` functions 
```{r}
glimpse(DF)
head(DF)
```
Exploratory data analysis

Use the `summary` function on the whole data frame to get summary statistics for each variable.

```{r}
summary(DF)
```
What did you see regarding what *should* be numeric variables?  What is the problem?

######
Numeric vars came in as character
######

There are 3 date variables in this data frame. Use the `lubridate` package that was introduced in the appendix of chapter 2 to convert td.photo, Start.Date, End.Date and Photo.Date to date formats and Photo.Time to a time format, retaining all of the detail as you go.

```{r}
library(lubridate)
DF$td.photo<-ymd_hms(DF$td.photo)
DF$Start.Date<-mdy(DF$Start.Date)
DF$End.Date<-mdy(DF$End.Date)
DF$Photo.Date<-mdy(DF$Photo.Date)
DF$Photo.Time<-hms(DF$Photo.Time)
```
Now use the dplyr verbs to do each of the following tasks:

1. Create a new data frame from just the columns Sampling.Unit.Name, ndays, and bin.  Name it whatever you want. Do it twice, first without piping, and the second time with piping.

```{r}
DF1<-select(DF, c(Sampling.Unit.Name,ndays, bin))
DF2<-DF %>% select(c(Sampling.Unit.Name,ndays, bin))
```

2. Determine how many unique species were detected during Round 1 of the study.

```{r}
#no new data frame
DF3<-DF %>% filter(round == 1) 
unique(DF3$bin)
```


3. Determine the total number of camera trap nights (ndays) in each round of the study. (Hint: group_by). Do this twice, once without piping and once with.

```{r}
#no piping
summarize(
  group_by(DF, round),
  totalNum = sum(ndays))

#with piping
DF %>% group_by(round) %>% summarize(
  totalNum = sum(ndays)
)
```

